Computational Methods for Principle Component Analysis Applied to Genotype Data

### 2018-06-20 doc/paper/paper.tex
Finish results for simulation study

For the simulation study
(\Cref{tbl:nChg-runtimes-ref}, \Cref{tbl:nChg-runtimes-study},
\Cref{tbl:nChg-accuracy-gold}, \Cref{tbl:nChg-accuracy-ctr},
\Cref{tbl:mChg-runtimes-study}),
we see that ADP, which is the most reliable method,
is the slowest in study runtimes.
By using the online SVD algorithm,
OADP achieved the highest accuracy (excluding ADP, which is the golden standard) and the fastest runtime.
SP is fast, also,
but its accuracy is the lowest.
By using the HDPCA package,
AP reduces the error of SP
and achieved the second highest in accuracy.
However, as the reference size increases,
the accuracies of different methods become closer and closer (\Cref{fig:nChg}).
As for the speed,
ADP's study runtime increases so fast with the reference size
that the study runtimes for the other methods seem to be constant in comparison (\Cref{fig:nChg}).
On the other hand,
the study runtimes appear to increase linearly with respect to the study size (\Cref{fig:mChg}).
This information can be used to predict the runtime for larger study samples.

@@

When we used the global samples,
we found that the PC scores predicted by the four methods' are almost identical.
The separation of the ethnic groups was clear,
and the shrinkage bias of SP was not obvious,
which is consistent with the theoretical understanding
that the shrinkage bias decreases
as the signal-to-noise ratio increases.

However, when we focus on the European (EUR) samples only,
the results given by SP were clearly unreliable.
The samples from British in England and Scotland (GBR)
and those from Utah residents with northern and western European ancestry	(CEU)
drifted very close to NULL.
This causes SP to incorrectly classified almost all of them as CEU,
since most GBR reference samples are far away from NULL.
A few of the study samples predicted by ADP to be GBR or CEU
were even classified as the Iberian population in Spain (IBS),
since the IBS reference samples are close to NULL.
Moreover, the shrinkage for the IBS
and for the Toscani in Italia (TSI) populations
caused significant errors within these two groups.
The IBS reference samples
are approximately in the middle
between the TSI reference samples and NULL.
Thus most of the the study samples predicted by ADP to be TSI
were classified by SP as IBS.

@@

\appendix

\section{Randomized SVD}\label{sec:randsvd}

\bibliographystyle{plainnat}
\bibliography{paper}

\section{Tables and Figures}

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|}
    \hline
    Method & Reference Complexity & Study Complexity \\ 
    \hline
    ADP & $\bO[n^2 p]$ & $\bO[mn(p + n^2)]$ \\
    \hline
    OADP & $\bO[n^2 p]$ & $\bO[mk(p + k n)]$ \\
    \hline
    SP & $\bO[n^2p]$ & $\bO[mkp]$ \\
    \hline
    AP & $\bO[n^2p]$ &  $\bO[mkp]$ \\
    \hline
  \end{tabular}
  \caption{
    Comparison of computational complexity for different methods.
    Here $p$ is the number of SNPs,
    $n$ is the number of individuals in the reference group,
    $m$ is the number of individuals in the  study group,
    and $k$ is the number of PCs calculated by the corresponding method.
  }
  \label{tbl:cplx}
\end{table}

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & Reference Runtimes (n=2492) & Study Runtimes (m=1000)& Golden Standard Error \\ 
    \hline
    ADP & 411 & 29813 & 0.00 \\
    \hline
    OADP & 2518 & 103 & 0.40 \\
    \hline
    SP & 411 & 425 & 1.95 \\
    \hline
    AP & 411 & 482 & 1.12 \\
    \hline
  \end{tabular}
  \caption{
    Comparison of runtimes and accuracy for different methods applied to the real-life datasets.
    The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals.
    The study sample contain 1000 individuals from the UKBioBank dataset.
    There are about 125,000 loci shared by the reference and study data.
    The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
  }
  \label{tbl:ukb}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        &  68  & 1263 & 2871 & 5720 & 9737 \\
    OADP       &  72  & 18   & 19   & 22   & 24   \\
    SP         &  68  & 26   & 42   & 67   & 96   \\
    AP         &  68  & 69   & 107  & 91   & 119  \\
    \hline
  \end{tabular}
  \caption{
    Reference runtimes for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-ref}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 391  &  130 &  222 &  339 &  486 \\
    OADP       & 15   &  136 &  230 &  350 &  499 \\
    SP         & 16   &  130 &  222 &  339 &  486 \\
    AP         & 34   &  130 &  222 &  339 &  486 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-study}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Study Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 0.00  & 0.00 & 0.00 & 0.00 & 0.00 \\
    OADP       & 0.23  & 0.15 & 0.11 & 0.08 & 0.07 \\
    SP         & 6.00  & 4.34 & 3.43 & 2.75 & 2.34 \\
    AP         & 0.46  & 0.37 & 0.31 & 0.26 & 0.22 \\
    \hline
  \end{tabular}
  \caption{
    Golden standard error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-gold}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 4.53  & 4.13 & 3.81 & 3.59 & 3.23 \\
    OADP       & 4.43  & 4.06 & 3.77 & 3.55 & 3.20 \\
    SP         & 5.79  & 4.51 & 3.89 & 3.56 & 3.19 \\
    AP         & 4.59  & 4.10 & 3.76 & 3.57 & 3.24 \\
    \hline
  \end{tabular}
  \caption{
    Geographic center error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-ctr}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 507  & 758 & 1011 & 1262 & 1549 \\
    OADP       &  73  & 108 &  156 &  189 &  282 \\
    SP         &  44  &  64 &   84 &  103 &  131 \\
    AP         &  66  &  81 &  100 &  117 &  146 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for the simulated data as the study size increases.
    The reference size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:mChg-runtimes-study}
\end{table}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_sp}
  \caption{EUR samples in UK Biobank data by SP}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_ap}
  \caption{EUR samples in UK Biobank data by AP}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_oadp}
  \caption{EUR samples in UK Biobank data by oadp}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_adp}
  \caption{EUR samples in UK Biobank data by adp}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{n1000}
  \caption{
    Predicted PC scores on top of reference PC scores.
    The four populations in the $2 \times 2$ grid simulated by the GGS software can be clearly identified.
    Reference individuals are in color,
    while predicted PC scores for the study individuals are in gray.
    Two measurements of deviations (accuracy) are used.
    The reference center error is the square root of the average squared distance between the study individuals and the population centers, which are the means of the PC scores of the reference individuals by the populations.
    The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
    The reference size is 1000 and the study size is 200.
    There are 100,000 loci (1000 per genealogy) and the migration rate is 100.
  }
  \label{fig:n1000}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb}
  \caption{
    The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals from 5 superpopulations: African, American, East Asian, European, and South Asian. 
    The study sample contain 1000 individuals from the UKBioBank dataset.
    There are about 125,000 loci shared by the reference and study data.
    The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
  }
  \label{fig:ukb}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{nChg}
  \caption{
    Runtimes and deviations for different methods as the reference sample size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{fig:nChg}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{mChg}
  \caption{
    Runtimes and deviations for different methods as the study sample size increases.
    The reference sample size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy).
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{fig:mChg}
\end{figure}

@@

>>>>

For the simulation study,
the PC scores predicted by AP, OADP, and ADP
are very close to each other
for every choice of reference sample size.
Compared to their results,
SP exhibits a strong shrinkage
when the reference sample size is 1000.
As we gradually increases the reference sample size to 3000
by an increment of 500,
the magnitude of the shrinkage decreases
but is still visible.
This is consistent with the theoretical result
that the shrinkage bias decreases
as the ratio of
the reference sample dimension to the reference sample size
decreases \citep{dey2016asymptotic}.

For computational cost,
we can see that the runtime for SP increases faster than linearly
as the reference sample size increases.
This is consistent
with the theoretical computational complexity of SP,
which expects the runtime to increase at the rate of $\bO[n^3]$.
In comparison, the runtimes of SP, AP, and OADP
increase only slightly.
The theoretical computational complexity of SP and AP is $\bO[1]$
and that of OADP is $\bO[n]$,
when the data dimension and the study sample size are fixed.

@@

When we used the global samples in the UK Biobank data,
we found that the PC scores predicted by the four methods' are almost identical.
The separation of the ethnic groups was clear,
and the shrinkage bias of SP was not obvious,
which is consistent with the theoretical understanding
that the shrinkage bias decreases
as the signal-to-noise ratio increases.

However, when we focused on the European (EUR) samples only,
the results given by SP were clearly unreliable.
The samples from British in England and Scotland (GBR)
and those from Utah residents with northern and western European ancestry	(CEU)
drifted very close to NULL.
This causes SP to incorrectly classified almost all of them as CEU,
since most GBR reference samples are far away from NULL.
A few of the study samples predicted by ADP to be GBR or CEU
were even classified as the Iberian population in Spain (IBS),
since the IBS reference samples are close to NULL.
Moreover, the shrinkage for the IBS
and for the Toscani in Italia (TSI) populations
caused significant errors within these two groups.
The IBS reference samples
are approximately in the middle
between the TSI reference samples and NULL.
Thus most of the the study samples predicted by ADP to be TSI
were classified by SP as IBS.

@@

\appendix
\bibliographystyle{plainnat}
\bibliography{paper}

\newpage
\section{Tables and Figures}

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|l|}
    \hline
    Method & Reference Complexity & Study Complexity \\ 
    \hline
    ADP & $\bO[n^2 p]$ & $\bO[mn(p + n^2)]$ \\
    \hline
    OADP & $\bO[n^2 p]$ & $\bO[mk(p + k n)]$ \\
    \hline
    SP & $\bO[n^2p]$ & $\bO[mkp]$ \\
    \hline
    AP & $\bO[n^2p]$ &  $\bO[mkp]$ \\
    \hline
  \end{tabular}
  \caption{
    Comparison of computational complexity for different methods.
    Here $p$ is the number of SNPs,
    $n$ is the number of individuals in the reference group,
    $m$ is the number of individuals in the  study group,
    and $k$ is the number of PCs calculated by the corresponding method.
  }
  \label{tbl:cplx}
\end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    \multicolumn{6}{|c|}{Study Runtime} \\
    \hline
    SP         &  17  & 17   & 16   & 18   & 18   \\
    AP         &  18  & 16   & 18  & 16   & 17  \\
    OADP       &  145  & 146   & 147   & 148   & 149   \\
    ADP        &  379  & 809 & 1526 & 2556 & 4062 \\
    \hline
    \multicolumn{6}{|c|}{Euclidean Error} \\
    \hline
    SP         &  188  & 139   & 112   & 91   & 84   \\
    AP         &  31  & 27   & 12  & 11   & 14  \\
    OADP       &  21  & 16   & 12   & 9   & 10   \\
    ADP        &  0  & 0 & 0 & 0 & 0 \\
    \hline
  \end{tabular}
  \caption{
    The runtimes and errors of the four methods
    as the reference size increases.
    Errors are measured as the Euclidean distance of
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
    }
\end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline
    Method & \multicolumn{2}{|c|}{Runtime} & \multicolumn{2}{|c|}{Error} \\
    & Global & European & Global & European \\
    \hline
    SP         &  62   & 48  &     & 450 \\ 
    AP         &  65   & 48  &     & 33  \\
    OADP       &  363  & 349 &     & 32  \\
    ADP        &  6745 & 518 &     & 0   \\
    \hline
  \end{tabular}
  \caption{
    The study runtimes (in seconds) and erros for the four methods
    for 500 randomly selected study samples
    in the UK Biobank data.
    Errors are measured as the Euclidean distance of
    the PC scores predicted by each method
    to those predicted by ADP.
    The 2492 samples from the 1000 Genomes data
    are used as the reference.
    The number of variants in common is 145,282.
    Only the top 4 PCs are calculated.
    }
\end{table}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ggsim_runtimes.png}
  \includegraphics[width=0.98\textwidth]{img/ggsim_errors.png}
  \caption{
    The runtimes (in seconds) and errors (Euclidean distance from ADP's PC scores) for the four methods
    as the reference size increases.
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
  }
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_adp}
  \caption{PC scores of 500 randomly selected global samples in UK Biobank data (circles) predicted by the four methods with the global samples in the 1000 Genomes data (squares) as the reference.}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_adp}
  \caption{PC scores of the European in the 500 randomly selected global samples UK Biobank data (circles) predicted by the four methods with the European samples in the 1000 Genomes data (squares) as the reference.}
\end{figure}

% \begin{figure}[p]
%   \centering
%   \includegraphics[width=0.98\textwidth]{n1000}
%   \caption{
%     Predicted PC scores on top of reference PC scores.
%     The four populations in the $2 \times 2$ grid simulated by the GGS software can be clearly identified.
%     Reference individuals are in color,
%     while predicted PC scores for the study individuals are in gray.
%     Two measurements of deviations (accuracy) are used.
%     The reference center error is the square root of the average squared distance between the study individuals and the population centers, which are the means of the PC scores of the reference individuals by the populations.
%     The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
%     The reference size is 1000 and the study size is 200.
%     There are 100,000 loci (1000 per genealogy) and the migration rate is 100.
%   }
%   \label{fig:n1000}
% \end{figure}

% \begin{figure}[p]
%   \centering
%   \includegraphics[width=0.98\textwidth]{ukb}
%   \caption{
%     The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals from 5 superpopulations: African, American, East Asian, European, and South Asian. 
%     The study sample contain 1000 individuals from the UKBioBank dataset.
%     There are about 125,000 loci shared by the reference and study data.
%     The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
%   }
%   \label{fig:ukb}
% \end{figure}

% \begin{figure}[p]
%   \centering
%   \includegraphics[width=0.98\textwidth]{img/nChg}
%   \caption{
%     Runtimes and deviations for different methods as the reference sample size increases.
%     The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{fig:nChg}
% \end{figure}

% \begin{figure}[p]
%   \centering
%   \includegraphics[width=0.98\textwidth]{img/mChg}
%   \caption{
%     Runtimes and deviations for different methods as the study sample size increases.
%     The reference sample size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy).
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{fig:mChg}
% \end{figure}

@@

% \begin{table} 
%   \centering
%   \begin{tabular}{|l|l|l|l|l|}
%     \hline
%     Method & Reference Runtimes (n=2492) & Study Runtimes (m=1000)& Golden Standard Error \\ 
%     \hline
%     ADP & 411 & 29813 & 0.00 \\
%     \hline
%     OADP & 2518 & 103 & 0.40 \\
%     \hline
%     SP & 411 & 425 & 1.95 \\
%     \hline
%     AP & 411 & 482 & 1.12 \\
%     \hline
%   \end{tabular}
%   \caption{
%     Comparison of runtimes and accuracy for different methods applied to the real-life datasets.
%     The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals.
%     The study sample contain 1000 individuals from the UKBioBank dataset.
%     There are about 125,000 loci shared by the reference and study data.
%     The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
%   }
%   \label{tbl:ukb}
% \end{table}

% \begin{table}
%   \centering
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%     Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
%     \hline
%     ADP        &  68  & 1263 & 2871 & 5720 & 9737 \\
%     OADP       &  72  & 18   & 19   & 22   & 24   \\
%     SP         &  68  & 26   & 42   & 67   & 96   \\
%     AP         &  68  & 69   & 107  & 91   & 119  \\
%     \hline
%   \end{tabular}
%   \caption{
%     Reference runtimes for the simulated data as the reference size increases.
%     The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{tbl:nChg-runtimes-ref}
% \end{table}

% \begin{table}
%   \centering
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%     Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
%     \hline
%     ADP        & 391  &  130 &  222 &  339 &  486 \\
%     OADP       & 15   &  136 &  230 &  350 &  499 \\
%     SP         & 16   &  130 &  222 &  339 &  486 \\
%     AP         & 34   &  130 &  222 &  339 &  486 \\
%     \hline
%   \end{tabular}
%   \caption{
%     Study runtimes for simulated data as the reference size increases.
%     The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{tbl:nChg-runtimes-study}
% \end{table}

% \begin{table}
%   \centering
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%     Study Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
%     \hline
%     ADP        & 0.00  & 0.00 & 0.00 & 0.00 & 0.00 \\
%     OADP       & 0.23  & 0.15 & 0.11 & 0.08 & 0.07 \\
%     SP         & 6.00  & 4.34 & 3.43 & 2.75 & 2.34 \\
%     AP         & 0.46  & 0.37 & 0.31 & 0.26 & 0.22 \\
%     \hline
%   \end{tabular}
%   \caption{
%     Golden standard error for the simulated data as the reference size increases.
%     The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{tbl:nChg-accuracy-gold}
% \end{table}

% \begin{table}
%   \centering
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%     Reference Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
%     \hline
%     ADP        & 4.53  & 4.13 & 3.81 & 3.59 & 3.23 \\
%     OADP       & 4.43  & 4.06 & 3.77 & 3.55 & 3.20 \\
%     SP         & 5.79  & 4.51 & 3.89 & 3.56 & 3.19 \\
%     AP         & 4.59  & 4.10 & 3.76 & 3.57 & 3.24 \\
%     \hline
%   \end{tabular}
%   \caption{
%     Geographic center error for the simulated data as the reference size increases.
%     The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{tbl:nChg-accuracy-ctr}
% \end{table}

% \begin{table}
%   \centering
%   \begin{tabular}{|l|l|l|l|l|l|}
%     \hline
%     Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
%     \hline
%     ADP        & 507  & 758 & 1011 & 1262 & 1549 \\
%     OADP       &  73  & 108 &  156 &  189 &  282 \\
%     SP         &  44  &  64 &   84 &  103 &  131 \\
%     AP         &  66  &  81 &  100 &  117 &  146 \\
%     \hline
%   \end{tabular}
%   \caption{
%     Study runtimes for the simulated data as the study size increases.
%     The reference size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy). 
%     Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
%   }
%   \label{tbl:mChg-runtimes-study}
% \end{table}

% \section{Randomized SVD}\label{sec:randsvd}
